An Elastica-driven Digital Curve Evolution Model for Image Segmentation\thanks{This work has been partially funded by CoMeDiC ANR-15-CE40-0006 research grant.}

### 2019-12-15 jmiv.tex
fix issue with \revision

\revision{
Given a digital shape $S \subset \Omega \subset \mathbb{Z}^2$, the goal is to compute a flow $S^{(i)}$ where $S^{(i+1)}$ has lower digital elastica $S^{(i)}$.

We observe that the integral invariant estimator \eqref{eq:curvature_approximation} is originaly designed to be evaluated on the digital boundary of some shape, which is the unknown of our problem. Injecting contour information leads to a third order model, which we prefer to avoid. Instead, we are going to exploit the II estimator definition in order to compute a flow that evolves proportionally to the squared curvature of the current shape.}

>>>>

\revision{
Given a digital shape $S \subset \Omega \subset \mathbb{Z}^2$, the goal is to compute a flow $S^{(i)}$ where $S^{(i+1)}$ has lower digital elastica $S^{(i)}$.}

\revision{We observe that the integral invariant estimator \eqref{eq:curvature_approximation} is originaly designed to be evaluated on the digital boundary of the shape, which is the unknown of our problem. Injecting contour information leads to a third order model, which we prefer to avoid. Instead, we are going to exploit the II estimator definition in order to compute a flow that evolves proportionally to the squared curvature of the current shape.}
